---
title: "Response_curves_top5_combined_climatic-soil_data_models"
author: "Laura J. Giraldo Kalil"
date: '2023-02-14'
output: html_document
---

This script summarizes the response curves for the "top 5" models
for each Damburneya species according to the environmental variables employed to build ecological niche models with MaxEnt.

It is based on the models generated in all other scripts
using climatic and edaphic data to model the niches of 
Damburneya species (D. ambigens, D. colorata, D. gentlei, D. salicifolia).

Those scripts are:
Combined climatic and edaphic data models:    "Model_Damb_bioclimsoil_02mar23.Rmd"
Climatic-only data models:                    "Model_Damb_bio_27feb23.Rmd"
Edaphic-only data models:                     "Model_Damb_soils_01mar23.Rmd"

It calls previously saved model files and the top 5 models previously chosen, based on delta AICc organized in decreasing order. It creates a summarized plot layout by species, and models type.

First, call the required libraries
```{r}

library(spocc)
library(spThin)
library(dismo)
library(rgeos)
library(ENMeval)
library(wallace)
library(here)
library(ggplot2)
library(gridExtra)
library(terra)
library(ade4)
library(dplyr)
library(gridtext)
library(cowplot)
library(ggpubr)
library(scales)
library(rcolorutils)
library(tidyverse)

```



Now, call the models for all the species. 
```{r}
model_Da_biosoils <- readRDS(here("Modelos","biosoils_modelos","ambigens","model_Da_biosoils.rds"))

model_Dc_biosoils <- readRDS(here("Modelos","biosoils_modelos","colorata","model_Dc_new_biosoils.rds"))

model_Dg_biosoils <- readRDS(here("Modelos","biosoils_modelos","gentlei","model_Dg_biosoils.rds"))

model_Ds_biosoils <- readRDS(here("Modelos","biosoils_modelos","salicifolia","model_Ds_biosoils.rds"))


```



#D. ambigens


Generate response plots and data for the top models
MaxEnt response plots for D. ambigens are created for the chosen top 5 best models:
Da_top1   fc.LQ_rm.1.5
Da_top2   fc.LQ_rm.2
Da_top3   fc.LQ_rm.2.5
Da_top4   fc.LQ_rm.1
Da_top5   fc.LQ_rm.3


Da_top1   fc.LQ_rm.1.5
```{r}
# Generate response plots for 1sth model for D. ambigens

pdf(here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top1.pdf"))
dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,col="#CC3311",main="Da_BS_top1_fc.LQ_rm.1.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
CECSOL_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
CLYPPT_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
NITROGEN_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
ORCDRC_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
PHIHOX_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")

Bio_1_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="Bio_1",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
Bio_4_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="Bio_4",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
Bio_12_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="Bio_12",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
Bio_14_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="Bio_14",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")
Bio_15_resp_Da_top1 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1.5,var="Bio_15",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. ambigens", top="top1" , model="BS", key="Da_BS_top1")



```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Da_BS <-rbind(AWCh_resp_Da_top1, CECSOL_resp_Da_top1,
                          CLYPPT_resp_Da_top1, NITROGEN_resp_Da_top1, 
                          ORCDRC_resp_Da_top1, PHIHOX_resp_Da_top1,
                          Bio_1_resp_Da_top1, Bio_4_resp_Da_top1,
                         Bio_12_resp_Da_top1, Bio_14_resp_Da_top1, 
                         Bio_15_resp_Da_top1) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top1_models_Da_BS[biosoils_cols] <- lapply(top1_models_Da_BS[biosoils_cols], factor)

#export response data
write.csv(top1_models_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top1.csv"))

#export model lambda

lambda_top1_Da_BS <- as.data.frame(model_Da_biosoils@models$fc.LQ_rm.1.5@lambdas)

write.csv(lambda_top1_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","lambda_Da_BS_top1.csv"))

```




Da_top2   fc.LQ_rm.2:
  
```{r}
# Generate response plots for 2nd model for D. ambigens

pdf(here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top2.pdf"))
dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,col="#CC3311",main="Da_BS_top2_fc.LQ_rm.2", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
CECSOL_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...)))  %>% mutate(var="CECSOL", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
CLYPPT_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
NITROGEN_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
ORCDRC_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")

PHIHOX_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")

Bio_1_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="Bio_1",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
Bio_4_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="Bio_4",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...)))  %>% mutate(var="Bio4", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
Bio_12_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="Bio_12",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
Bio_14_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="Bio_14",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")
Bio_15_resp_Da_top2 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2,var="Bio_15",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. ambigens", top="top2" , model="BS", key="Da_BS_top2")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Da_BS <-rbind(AWCh_resp_Da_top2, CECSOL_resp_Da_top2,
                          CLYPPT_resp_Da_top2, NITROGEN_resp_Da_top2, 
                          ORCDRC_resp_Da_top2, PHIHOX_resp_Da_top2,
                          Bio_1_resp_Da_top2, Bio_4_resp_Da_top2,
                        Bio_12_resp_Da_top2, Bio_14_resp_Da_top2, 
                        Bio_15_resp_Da_top2) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top2_models_Da_BS[biosoils_cols] <- lapply(top2_models_Da_BS[biosoils_cols], factor)

#export response data
write.csv(top2_models_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top2.csv"))

#export model lambda

lambda_top2_Da_BS <- as.data.frame(model_Da_biosoils@models$fc.LQ_rm.2@lambdas)

write.csv(lambda_top2_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","lambda_Da_BS_top2.csv"))

```


Da_top3   fc.LQ_rm.2.5:
  
```{r}
# Generate response plots for 3rd model for D. ambigens

pdf(here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top3.pdf"))
dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,col="#CC3311",main="Da_BS_top3_fc.LQ_rm.2.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
CECSOL_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
CLYPPT_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
NITROGEN_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
ORCDRC_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")

PHIHOX_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")

Bio_1_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="Bio_1",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
Bio_4_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="Bio_4",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
Bio_12_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="Bio_12",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
Bio_14_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="Bio_14",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")
Bio_15_resp_Da_top3 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.2.5,var="Bio_15",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. ambigens", top="top3" , model="BS", key="Da_BS_top3")



```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Da_BS <-rbind(AWCh_resp_Da_top3, CECSOL_resp_Da_top3,
                          CLYPPT_resp_Da_top3, NITROGEN_resp_Da_top3, 
                          ORCDRC_resp_Da_top3, PHIHOX_resp_Da_top3,
                          Bio_1_resp_Da_top3, Bio_4_resp_Da_top3,
                        Bio_12_resp_Da_top3, Bio_14_resp_Da_top3, 
                        Bio_15_resp_Da_top3) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top3_models_Da_BS[biosoils_cols] <- lapply(top3_models_Da_BS[biosoils_cols], factor)

#export response data
write.csv(top3_models_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top3.csv"))

#export model lambda

lambda_top3_Da_BS <- as.data.frame(model_Da_biosoils@models$fc.LQ_rm.2.5@lambdas)

write.csv(lambda_top3_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","lambda_Da_BS_top3.csv"))

```


Da_top4   fc.LQ_rm.1

```{r}
# Generate response plots for 4th model for D. ambigens

pdf(here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top4.pdf"))
dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,col="#CC3311",main="Da_BS_top4_fc.LQ_rm.1", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
CECSOL_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
CLYPPT_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
NITROGEN_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
ORCDRC_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")

PHIHOX_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")

Bio_1_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="Bio_1",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
Bio_4_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="Bio_4",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
Bio_12_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="Bio_12",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
Bio_14_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="Bio_14",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")
Bio_15_resp_Da_top4 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.1,var="Bio_15",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. ambigens", top="top4" , model="BS", key="Da_BS_top4")



```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Da_BS <-rbind(AWCh_resp_Da_top4, CECSOL_resp_Da_top4,
                          CLYPPT_resp_Da_top4, NITROGEN_resp_Da_top4, 
                          ORCDRC_resp_Da_top4, PHIHOX_resp_Da_top4,
                          Bio_1_resp_Da_top4, Bio_4_resp_Da_top4,
                        Bio_12_resp_Da_top4, Bio_14_resp_Da_top4, 
                        Bio_15_resp_Da_top4) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top4_models_Da_BS[biosoils_cols] <- lapply(top4_models_Da_BS[biosoils_cols], factor)

#export response data
write.csv(top4_models_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top4.csv"))

#export model lambda
lambda_top4_Da_BS <- as.data.frame(model_Da_biosoils@models$fc.LQ_rm.1@lambdas)

write.csv(lambda_top4_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","lambda_Da_BS_top4.csv"))

```







Da_top5   fc.LQ_rm.3

```{r}
# Generate response plots for 5th model for D. ambigens

pdf(here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top5.pdf"))
dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,col="#CC3311",main="Da_BS_top5_fc.LQ_rm.3", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
CECSOL_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
CLYPPT_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
NITROGEN_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
ORCDRC_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")

PHIHOX_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")


Bio_1_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="Bio_1",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
Bio_4_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="Bio_4",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
Bio_12_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="Bio_12",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
Bio_14_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="Bio_14",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")
Bio_15_resp_Da_top5 <- as.data.frame(dismo::response(
  model_Da_biosoils@models$fc.LQ_rm.3,var="Bio_15",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. ambigens", top="top5" , model="BS", key="Da_BS_top5")


```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Da_BS <-rbind(AWCh_resp_Da_top5, CECSOL_resp_Da_top5,
                          CLYPPT_resp_Da_top5, NITROGEN_resp_Da_top5, 
                          ORCDRC_resp_Da_top5, PHIHOX_resp_Da_top5,
                          Bio_1_resp_Da_top5, Bio_4_resp_Da_top5,
                        Bio_12_resp_Da_top5, Bio_14_resp_Da_top5, 
                        Bio_15_resp_Da_top5) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top5_models_Da_BS[biosoils_cols] <- lapply(top5_models_Da_BS[biosoils_cols], factor)

#export response data
write.csv(top5_models_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","resp_Da_BS_top5.csv"))

#export model lambda

lambda_top5_Da_BS <- as.data.frame(model_Da_biosoils@models$fc.LQ_rm.3@lambdas)

write.csv(lambda_top5_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","lambda_Da_BS_top5.csv"))

```


Create and export a single data frame with all response curves data of the top 5 models for D. ambigens
```{r}

top_models_Da_BS <-rbind(top1_models_Da_BS,top2_models_Da_BS,
                        top3_models_Da_BS,top4_models_Da_BS,top5_models_Da_BS)

write.csv(top_models_Da_BS, here("Modelos","biosoils_modelos","ambigens","top_Da_BS","top_models_Da_BS.csv"))

```

#D. colorata

Generate response plots and data for the top models
MaxEnt response plots for D. colorata are created for the chosen top 5 best models:

Dc_top1		fc.LQP_rm.4
Dc_top2		fc.LQHP_rm.3.5
Dc_top3		fc.LQP_rm.3.5
Dc_top4		fc.LQHP_rm.3
Dc_top5		fc.LQ_rm.3.5



Dc_top1		fc.LQP_rm.4
```{r}
# Generate response plots for 1sth model for D. colorata

pdf(here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top1.pdf"))
dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,col="#4477AA",main="Dc_BS_top1_fc.LQP_rm.4", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

CECSOL_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

CLYPPT_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

NITROGEN_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

ORCDRC_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

PHIHOX_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

Bio_1_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="Bio_1",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")
Bio_4_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="Bio_4",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")
Bio_12_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="Bio_12",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")
Bio_14_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="Bio_14",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")
Bio_15_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.4,var="Bio_15",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. colorata", top="top1" , model="BS", key="Dc_BS_top1")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Dc_BS <-rbind(AWCh_resp_Dc_top1, CECSOL_resp_Dc_top1,
                          CLYPPT_resp_Dc_top1, NITROGEN_resp_Dc_top1, 
                          ORCDRC_resp_Dc_top1, PHIHOX_resp_Dc_top1,
                          Bio_1_resp_Dc_top1, Bio_4_resp_Dc_top1,
                         Bio_12_resp_Dc_top1, Bio_14_resp_Dc_top1, 
                         Bio_15_resp_Dc_top1) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top1_models_Dc_BS[biosoils_cols] <- lapply(top1_models_Dc_BS[biosoils_cols], factor)

#export response data
write.csv(top1_models_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top1.csv"))

#export model lambda

lambDc_top1_Dc_BS <- as.data.frame(model_Dc_biosoils@models$fc.LQP_rm.4@lambdas)

write.csv(lambDc_top1_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","lambDc_Dc_new_BS_top1.csv"))

```


Dc_top2		fc.LQHP_rm.3.5
```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top2.pdf"))
dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,col="#4477AA",main="Dc_BS_top2_fc.LQHP_rm.3.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
CECSOL_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
CLYPPT_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
NITROGEN_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
ORCDRC_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
PHIHOX_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")


Bio_1_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="Bio_1",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
Bio_4_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="Bio_4",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
Bio_12_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="Bio_12",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
Bio_14_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="Bio_14",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")
Bio_15_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3.5,var="Bio_15",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. colorata", top="top2" , model="BS", key="Dc_BS_top2")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Dc_BS <-rbind(AWCh_resp_Dc_top2, CECSOL_resp_Dc_top2,
                          CLYPPT_resp_Dc_top2, NITROGEN_resp_Dc_top2, 
                          ORCDRC_resp_Dc_top2, PHIHOX_resp_Dc_top2,
                          Bio_1_resp_Dc_top2, Bio_4_resp_Dc_top2,
                         Bio_12_resp_Dc_top2, Bio_14_resp_Dc_top2, 
                         Bio_15_resp_Dc_top2) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top2_models_Dc_BS[biosoils_cols] <- lapply(top2_models_Dc_BS[biosoils_cols], factor)

#export response data
write.csv(top2_models_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top2.csv"))

#export model lambda

lambDc_top2_Dc_BS <- as.data.frame(model_Dc_biosoils@models$fc.LQHP_rm.3.5@lambdas)

write.csv(lambDc_top2_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","lambDc_Dc_new_BS_top2.csv"))

```


Dc_top3		fc.LQP_rm.3.5
```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top3.pdf"))
dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,col="#4477AA",main="Dc_BS_top3_fc.LQP_rm.3.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
CECSOL_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
CLYPPT_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
NITROGEN_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
ORCDRC_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
PHIHOX_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")

Bio_1_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="Bio_1",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
Bio_4_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="Bio_4",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
Bio_12_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="Bio_12",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
Bio_14_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="Bio_14",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
Bio_15_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQP_rm.3.5,var="Bio_15",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. colorata", top="top3" , model="BS", key="Dc_BS_top3")
```





Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Dc_BS <-rbind(AWCh_resp_Dc_top3, CECSOL_resp_Dc_top3,
                          CLYPPT_resp_Dc_top3, NITROGEN_resp_Dc_top3, 
                          ORCDRC_resp_Dc_top3, PHIHOX_resp_Dc_top3,
                          Bio_1_resp_Dc_top3, Bio_4_resp_Dc_top3,
                         Bio_12_resp_Dc_top3, Bio_14_resp_Dc_top3, 
                         Bio_15_resp_Dc_top3) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top3_models_Dc_BS[biosoils_cols] <- lapply(top3_models_Dc_BS[biosoils_cols], factor)

#export response data
write.csv(top3_models_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top3.csv"))

#export model lambda

lambDc_top3_Dc_BS <- as.data.frame(model_Dc_biosoils@models$fc.LQP_rm.3.5@lambdas)

write.csv(lambDc_top3_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","lambDc_Dc_new_BS_top3.csv"))

```


Dc_top4		fc.LQHP_rm.3
```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top4.pdf"))
dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,col="#4477AA",main="Dc_BS_top4_fc.LQHP_rm.3", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
CECSOL_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
CLYPPT_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
NITROGEN_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
ORCDRC_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
PHIHOX_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")

Bio_1_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="Bio_1",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
Bio_4_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="Bio_4",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
Bio_12_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="Bio_12",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
Bio_14_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="Bio_14",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")
Bio_15_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQHP_rm.3,var="Bio_15",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. colorata", top="top4" , model="BS", key="Dc_BS_top4")


```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Dc_BS <-rbind(AWCh_resp_Dc_top4, CECSOL_resp_Dc_top4,
                          CLYPPT_resp_Dc_top4, NITROGEN_resp_Dc_top4, 
                          ORCDRC_resp_Dc_top4, PHIHOX_resp_Dc_top4,
                          Bio_1_resp_Dc_top4, Bio_4_resp_Dc_top4,
                         Bio_12_resp_Dc_top4, Bio_14_resp_Dc_top4, 
                         Bio_15_resp_Dc_top4) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top4_models_Dc_BS[biosoils_cols] <- lapply(top4_models_Dc_BS[biosoils_cols], factor)

#export response data
write.csv(top4_models_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top4.csv"))

#export model lambda

lambDc_top4_Dc_BS <- as.data.frame(model_Dc_biosoils@models$fc.LQHP_rm.3@lambdas)

write.csv(lambDc_top4_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","lambDc_Dc_new_BS_top4.csv"))

```




Dc_top5		fc.LQ_rm.3.5

```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top5.pdf"))
dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,col="#4477AA",main="Dc_BS_top5_fc.LQ_rm.3.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
CECSOL_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
CLYPPT_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
NITROGEN_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
ORCDRC_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
PHIHOX_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
Bio_1_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="Bio_1",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
Bio_4_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="Bio_4",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
Bio_12_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="Bio_12",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
Bio_14_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="Bio_14",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")
Bio_15_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_biosoils@models$fc.LQ_rm.3.5,var="Bio_15",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. colorata", top="top5" , model="BS", key="Dc_BS_top5")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Dc_BS <-rbind(AWCh_resp_Dc_top5, CECSOL_resp_Dc_top5,
                          CLYPPT_resp_Dc_top5, NITROGEN_resp_Dc_top5, 
                          ORCDRC_resp_Dc_top5, PHIHOX_resp_Dc_top5,
                          Bio_1_resp_Dc_top5, Bio_4_resp_Dc_top5,
                         Bio_12_resp_Dc_top5, Bio_14_resp_Dc_top5, 
                         Bio_15_resp_Dc_top5) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top5_models_Dc_BS[biosoils_cols] <- lapply(top5_models_Dc_BS[biosoils_cols], factor)

#export response data
write.csv(top5_models_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","resp_Dc_new_BS_top5.csv"))

#export model lambda

lambDc_top5_Dc_BS <- as.data.frame(model_Dc_biosoils@models$fc.LQ_rm.3.5@lambdas)

write.csv(lambDc_top5_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","lambDc_Dc_new_BS_top5.csv"))

```




Create and export a single data frame with all response curves data of the top 5 models for D. colorata
```{r}

top_models_Dc_BS <-rbind(top1_models_Dc_BS,top2_models_Dc_BS,
                         top3_models_Dc_BS,top4_models_Dc_BS,top5_models_Dc_BS)

write.csv(top_models_Dc_BS, here("Modelos","biosoils_modelos","colorata","top_Dc_BS","top_models_Dc_new_BS.csv"))

```



# D. gentlei
Generate response plots and data for the top models
MaxEnt response plots for D. gentlei are created for the chosen top 5 best models:

Dg_top1   fc.LQH_rm.2.5
Dg_top2   fc.LQH_rm.3.5
Dg_top3   fc.LQHP_rm.4
Dg_top4   fc.LQH_rm.4
Dg_top5   fc.LQHP_rm.2.5


Dg_top1   fc.LQH_rm.2.5

```{r}
# Generate response plots for 1sth model for D. gentlei

pdf(here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top1.pdf"))
dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,col="#DDAA33", main="Dg_BS_top1_fc.LQH_rm.2.5",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
CECSOL_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
CLYPPT_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
NITROGEN_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
ORCDRC_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
PHIHOX_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
Bio_1_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="Bio_1",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
Bio_4_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="Bio_4",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
Bio_12_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="Bio_12",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
Bio_14_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="Bio_14",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")
Bio_15_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.2.5,var="Bio_15",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. gentlei", top="top1" , model="BS", key="Dg_BS_top1")



```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Dg_BS <-rbind(AWCh_resp_Dg_top1, CECSOL_resp_Dg_top1,
                          CLYPPT_resp_Dg_top1, NITROGEN_resp_Dg_top1, 
                          ORCDRC_resp_Dg_top1, PHIHOX_resp_Dg_top1,
                          Bio_1_resp_Dg_top1, Bio_4_resp_Dg_top1,
                        Bio_12_resp_Dg_top1, Bio_14_resp_Dg_top1, 
                        Bio_15_resp_Dg_top1) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top1_models_Dg_BS[biosoils_cols] <- lapply(top1_models_Dg_BS[biosoils_cols], factor)

#export response data
write.csv(top1_models_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top1.csv"))

#export model lambda

lambda_top1_Dg_BS <- as.data.frame(model_Dg_biosoils@models$fc.LQH_rm.2.5@lambdas)

write.csv(lambda_top1_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","lambda_Dg_BS_top1.csv"))

```




Dg_top2   fc.LQH_rm.3.5:
```{r}
# Generate response plots for 2nd model for D. gentlei

pdf(here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top2.pdf"))
dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,col="#DDAA33", main="Dg_BS_top2_fc.LQH_rm.3.5",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
CECSOL_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
CLYPPT_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
NITROGEN_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
ORCDRC_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
PHIHOX_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")

Bio_1_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="Bio_1",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
Bio_4_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="Bio_4",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
Bio_12_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="Bio_12",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
Bio_14_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="Bio_14",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")
Bio_15_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.3.5,var="Bio_15",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. gentlei", top="top2" , model="BS", key="Dg_BS_top2")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Dg_BS <-rbind(AWCh_resp_Dg_top2, CECSOL_resp_Dg_top2,
                          CLYPPT_resp_Dg_top2, NITROGEN_resp_Dg_top2, 
                          ORCDRC_resp_Dg_top2, PHIHOX_resp_Dg_top2,
                          Bio_1_resp_Dg_top2, Bio_4_resp_Dg_top2,
                        Bio_12_resp_Dg_top2, Bio_14_resp_Dg_top2, 
                        Bio_15_resp_Dg_top2) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top2_models_Dg_BS[biosoils_cols] <- lapply(top2_models_Dg_BS[biosoils_cols], factor)

#export response data
write.csv(top2_models_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top2.csv"))

#export model lambda

lambda_top2_Dg_BS <- as.data.frame(model_Dg_biosoils@models$fc.LQH_rm.3.5@lambdas)

write.csv(lambda_top2_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","lambda_Dg_BS_top2.csv"))

```



Dg_top3   fc.LQHP_rm.4:
```{r}
# Generate response plots for 3rd model for D. gentlei

pdf(here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top3.pdf"))
dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,col="#DDAA33", main="Dg_BS_top3_fc.LQHP_rm.4",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
CECSOL_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
CLYPPT_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
NITROGEN_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
ORCDRC_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
PHIHOX_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")

Bio_1_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="Bio_1",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
Bio_4_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="Bio_4",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
Bio_12_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="Bio_12",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
Bio_14_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="Bio_14",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")
Bio_15_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.4,var="Bio_15",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. gentlei", top="top3" , model="BS", key="Dg_BS_top3")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Dg_BS <-rbind(AWCh_resp_Dg_top3, CECSOL_resp_Dg_top3,
                          CLYPPT_resp_Dg_top3, NITROGEN_resp_Dg_top3, 
                          ORCDRC_resp_Dg_top3, PHIHOX_resp_Dg_top3,
                          Bio_1_resp_Dg_top3, Bio_4_resp_Dg_top3,
                        Bio_12_resp_Dg_top3, Bio_14_resp_Dg_top3, 
                        Bio_15_resp_Dg_top3) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top3_models_Dg_BS[biosoils_cols] <- lapply(top3_models_Dg_BS[biosoils_cols], factor)

#export response data
write.csv(top3_models_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top3.csv"))

#export model lambda

lambda_top3_Dg_BS <- as.data.frame(model_Dg_biosoils@models$fc.LQHP_rm.4@lambdas)

write.csv(lambda_top3_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","lambda_Dg_BS_top3.csv"))

```


Dg_top4   fc.LQH_rm.4:
```{r}
# Generate response plots for 4th model for D. gentlei

pdf(here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top4.pdf"))
dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,col="#DDAA33", main="Dg_BS_top4_fc.LQH_rm.4",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
CECSOL_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
CLYPPT_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
NITROGEN_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
ORCDRC_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
PHIHOX_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")

Bio_1_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="Bio_1",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
Bio_4_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="Bio_4",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
Bio_12_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="Bio_12",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
Bio_14_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="Bio_14",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")
Bio_15_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQH_rm.4,var="Bio_15",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. gentlei", top="top4" , model="BS", key="Dg_BS_top4")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Dg_BS <-rbind(AWCh_resp_Dg_top4, CECSOL_resp_Dg_top4,
                          CLYPPT_resp_Dg_top4, NITROGEN_resp_Dg_top4, 
                          ORCDRC_resp_Dg_top4, PHIHOX_resp_Dg_top4,
                          Bio_1_resp_Dg_top4, Bio_4_resp_Dg_top4,
                        Bio_12_resp_Dg_top4, Bio_14_resp_Dg_top4, 
                        Bio_15_resp_Dg_top4) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top4_models_Dg_BS[biosoils_cols] <- lapply(top4_models_Dg_BS[biosoils_cols], factor)

#export response data
write.csv(top4_models_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top4.csv"))

#export model lambda

lambda_top4_Dg_BS <- as.data.frame(model_Dg_biosoils@models$fc.LQH_rm.4@lambdas)

write.csv(lambda_top4_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","lambda_Dg_BS_top4.csv"))

```


Dg_top5   fc.LQHP_rm.2.5:
```{r}
# Generate response plots for 5th model for D. gentlei

pdf(here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top5.pdf"))
dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,col="#DDAA33", main="Dg_BS_top5_fc.LQHP_rm.2.5",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
CECSOL_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
CLYPPT_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
NITROGEN_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
ORCDRC_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
PHIHOX_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")

Bio_1_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="Bio_1",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
Bio_4_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="Bio_4",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
Bio_12_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="Bio_12",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
Bio_14_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="Bio_14",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")
Bio_15_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_biosoils@models$fc.LQHP_rm.2.5,var="Bio_15",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. gentlei", top="top5" , model="BS", key="Dg_BS_top5")



```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Dg_BS <-rbind(AWCh_resp_Dg_top5, CECSOL_resp_Dg_top5,
                          CLYPPT_resp_Dg_top5, NITROGEN_resp_Dg_top5, 
                          ORCDRC_resp_Dg_top5, PHIHOX_resp_Dg_top5,
                          Bio_1_resp_Dg_top5, Bio_4_resp_Dg_top5,
                        Bio_12_resp_Dg_top5, Bio_14_resp_Dg_top5, 
                        Bio_15_resp_Dg_top5) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top5_models_Dg_BS[biosoils_cols] <- lapply(top5_models_Dg_BS[biosoils_cols], factor)

#export response data
write.csv(top5_models_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","resp_Dg_BS_top5.csv"))

#export model lambda

lambda_top5_Dg_BS <- as.data.frame(model_Dg_biosoils@models$fc.LQHP_rm.2.5@lambdas)

write.csv(lambda_top5_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","lambda_Dg_BS_top5.csv"))

```


Create and export a single data frame with all response curves data of the top 5 models for D. gentlei
```{r}

top_models_Dg_BS <-rbind(top1_models_Dg_BS,top2_models_Dg_BS,
                        top3_models_Dg_BS,top4_models_Dg_BS,top5_models_Dg_BS)

write.csv(top_models_Dg_BS, here("Modelos","biosoils_modelos","gentlei","top_Dg_BS","top_models_Dg_BS.csv"))

```



#D. salicifolia
Generate response plots and data for the top models
MaxEnt response plots for D. salicifolia are created for the chosen top 5 best models:












Ds_top1   fc.LQHP_rm.1.5:
  
```{r}

pdf(here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top1.pdf"))
dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
CECSOL_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
CLYPPT_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
NITROGEN_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
ORCDRC_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
PHIHOX_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")

Bio_1_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="Bio_1",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
Bio_4_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="Bio_4",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
Bio_12_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="Bio_12",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
Bio_14_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="Bio_14",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")
Bio_15_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.1.5,var="Bio_15",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. salicifolia", top="top1" , model="BS", key="Ds_BS_top1")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Ds_BS <-rbind(AWCh_resp_Ds_top1, CECSOL_resp_Ds_top1,
                         CLYPPT_resp_Ds_top1, NITROGEN_resp_Ds_top1, 
                         ORCDRC_resp_Ds_top1, PHIHOX_resp_Ds_top1,
                         Bio_1_resp_Ds_top1, Bio_4_resp_Ds_top1,
                        Bio_12_resp_Ds_top1, Bio_14_resp_Ds_top1, 
                        Bio_15_resp_Ds_top1) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top1_models_Ds_BS[biosoils_cols] <- lapply(top1_models_Ds_BS[biosoils_cols], factor)

#export response data
write.csv(top1_models_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top1.csv"))

#export model lambda

lambda_top1_Ds_BS <- as.data.frame(model_Ds_biosoils@models$fc.LQHP_rm.1.5@lambdas)

write.csv(lambda_top1_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","lambda_Ds_BS_top1.csv"))

```


Ds_top2   fc.LQHP_rm.2.5:
  
```{r}
pdf(here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top2.pdf"))
dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
CECSOL_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
CLYPPT_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
NITROGEN_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
ORCDRC_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
PHIHOX_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")

Bio_1_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="Bio_1",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
Bio_4_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="Bio_4",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
Bio_12_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="Bio_12",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
Bio_14_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="Bio_14",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")
Bio_15_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2.5
  ,var="Bio_15",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. salicifolia", top="top2" , model="BS", key="Ds_BS_top2")

```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Ds_BS <-rbind(AWCh_resp_Ds_top2, CECSOL_resp_Ds_top2,
                          CLYPPT_resp_Ds_top2, NITROGEN_resp_Ds_top2, 
                          ORCDRC_resp_Ds_top2, PHIHOX_resp_Ds_top2,
                          Bio_1_resp_Ds_top2, Bio_4_resp_Ds_top2,
                        Bio_12_resp_Ds_top2, Bio_14_resp_Ds_top2, 
                        Bio_15_resp_Ds_top2) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top2_models_Ds_BS[biosoils_cols] <- lapply(top2_models_Ds_BS[biosoils_cols], factor)

#export response data
write.csv(top2_models_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top2.csv"))

#export model lambda

lambda_top2_Ds_BS <- as.data.frame(model_Ds_biosoils@models$fc.LQHP_rm.2.5@lambdas)

write.csv(lambda_top2_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","lambda_Ds_BS_top2.csv"))

```




Ds_top3   fc.LQHP_rm.3:
  
```{r}

pdf(here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top3.pdf"))
dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
CECSOL_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
CLYPPT_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
NITROGEN_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
ORCDRC_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
PHIHOX_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")

Bio_1_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="Bio_1",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
Bio_4_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="Bio_4",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
Bio_12_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="Bio_12",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
Bio_14_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="Bio_14",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")
Bio_15_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.3
  ,var="Bio_15",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. salicifolia", top="top3" , model="BS", key="Ds_BS_top3")


```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Ds_BS <-rbind(AWCh_resp_Ds_top3, CECSOL_resp_Ds_top3,
                          CLYPPT_resp_Ds_top3, NITROGEN_resp_Ds_top3, 
                          ORCDRC_resp_Ds_top3, PHIHOX_resp_Ds_top3,
                          Bio_1_resp_Ds_top3, Bio_4_resp_Ds_top3,
                        Bio_12_resp_Ds_top3, Bio_14_resp_Ds_top3, 
                        Bio_15_resp_Ds_top3) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top3_models_Ds_BS[biosoils_cols] <- lapply(top3_models_Ds_BS[biosoils_cols], factor)

#export response data
write.csv(top3_models_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top3.csv"))

#export model lambda

lambda_top3_Ds_BS <- as.data.frame(model_Ds_biosoils@models$fc.LQHP_rm.3@lambdas)

write.csv(lambda_top3_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","lambda_Ds_BS_top3.csv"))

```









Ds_top4   fc.LQHP_rm.2:
  
```{r}
pdf(here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top4.pdf"))
dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
CECSOL_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
CLYPPT_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
NITROGEN_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
ORCDRC_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
PHIHOX_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")

Bio_1_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="Bio_1",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
Bio_4_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="Bio_4",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
Bio_12_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="Bio_12",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
Bio_14_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="Bio_14",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")
Bio_15_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.2
  ,var="Bio_15",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. salicifolia", top="top4" , model="BS", key="Ds_BS_top4")


```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Ds_BS <-rbind(AWCh_resp_Ds_top4, CECSOL_resp_Ds_top4,
                         CLYPPT_resp_Ds_top4, NITROGEN_resp_Ds_top4, 
                         ORCDRC_resp_Ds_top4, PHIHOX_resp_Ds_top4,
                         Bio_1_resp_Ds_top4, Bio_4_resp_Ds_top4,
                        Bio_12_resp_Ds_top4, Bio_14_resp_Ds_top4, 
                        Bio_15_resp_Ds_top4) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top4_models_Ds_BS[biosoils_cols] <- lapply(top4_models_Ds_BS[biosoils_cols], factor)

#export response data
write.csv(top4_models_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top4.csv"))

#export model lambda

lambda_top4_Ds_BS <- as.data.frame(model_Ds_biosoils@models$fc.LQHP_rm.2@lambdas)

write.csv(lambda_top4_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","lambda_Ds_BS_top4.csv"))

```



Ds_top5   fc.LQHP_rm.4:
  
```{r}
pdf(here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top5.pdf"))
dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
CECSOL_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
CLYPPT_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
NITROGEN_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
ORCDRC_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
PHIHOX_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")

Bio_1_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="Bio_1",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio1", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
Bio_4_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="Bio_4",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio4", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
Bio_12_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="Bio_12",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio12", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
Bio_14_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="Bio_14",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio14", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")
Bio_15_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_biosoils@models$fc.LQHP_rm.4
  ,var="Bio_15",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="Bio15", species="D. salicifolia", top="top5" , model="BS", key="Ds_BS_top5")

```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Ds_BS <-rbind(AWCh_resp_Ds_top5, CECSOL_resp_Ds_top5,
                          CLYPPT_resp_Ds_top5, NITROGEN_resp_Ds_top5, 
                          ORCDRC_resp_Ds_top5, PHIHOX_resp_Ds_top5,
                          Bio_1_resp_Ds_top5, Bio_4_resp_Ds_top5,
                        Bio_12_resp_Ds_top5, Bio_14_resp_Ds_top5, 
                        Bio_15_resp_Ds_top5) 

#factorize categorical columns
biosoils_cols <- c("var","species","top","model","key")
top5_models_Ds_BS[biosoils_cols] <- lapply(top5_models_Ds_BS[biosoils_cols], factor)

#export response data
write.csv(top5_models_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","resp_Ds_BS_top5.csv"))

#export model lambda

lambda_top5_Ds_BS <- as.data.frame(model_Ds_biosoils@models$fc.LQHP_rm.4@lambdas)

write.csv(lambda_top5_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","lambda_Ds_BS_top5.csv"))

```


Create and export a single data frame with all response curves data of the top 5 models for D. salicifolia
```{r}

top_models_Ds_BS <-rbind(top1_models_Ds_BS,top2_models_Ds_BS,
                        top3_models_Ds_BS,top4_models_Ds_BS,top5_models_Ds_BS)

write.csv(top_models_Ds_BS, here("Modelos","biosoils_modelos","salicifolia","top_Ds_BS","top_models_Ds_BS.csv"))

```



Create and export a single data frame with all response curves data of the top 5 models for all species
```{r}
#concatenate all models for all species in a single dataframe
top_models_all_BS <-rbind(top_models_Da_BS,
                         top_models_Dc_BS,
                         top_models_Dg_BS,
                         top_models_Ds_BS)

write.csv(top_models_all_BS,here("Modelos","biosoils_modelos",
                         "resp_top_models_all_new_BS.csv"))

```

Edit data frame for plotting
```{r}

#top_models_all_BS <- 
 # read.csv(here("Modelos","biosoils_modelos",
  #                       "resp_top_models_all_new_BS.csv"))

#add the model name to the top 5 models based on a summary file
library(readxl)
tmp_BS_Summary_top <- read_xlsx(here("Modelos","TOP_modelos", "Resumen_top5_modelos.xlsx"))
colnames(tmp_BS_Summary_top)

cols_tmp <- c("ID","Model_data","model_key","Species","sp_key",
              "fc","rm","top","tune.args","key")
tmp_BS_Summary_top[cols_tmp] <- lapply(tmp_BS_Summary_top[cols_tmp], factor)


tmp_models <- subset(tmp_BS_Summary_top, Model_data %in% c("Climatic-only"))
tmp_models <- tmp_models[,c("key","tune.args")]

#Call the top5 response dataframe and add columns with model name

top_models_all_BS <- 
  left_join(top_models_all_BS,tmp_models, by="key")

```


## Response plots edition
Response plot layout of the top 5 models by species and model, in ggplot



Create de plots for each variable with a plotting function


```{r}
#Reorder variables to avoid alphabetic order display

#top_models_all_BS <- read.csv(here(
 # "Modelos","biosoils_modelos","resp_top_models_all_BS.csv"))

neworder <- c("AWCh","CECSOL","CLYPPT","NITROGEN","ORCDRC","PHIHOX",
              "Bio1","Bio4","Bio12","Bio14","Bio15")

datos <- arrange(transform(top_models_all_BS,
                           var=factor(var,levels=neworder)),var)



cols_tmp <- c("model","species","key",
             "top","tune.args")
datos[cols_tmp] <- lapply(datos[cols_tmp], factor)

# exclude data below or above the desired range in the layout
library(skimr)
skim(datos)

#exclude values lower than 0
datos <- datos[datos$V1 >= 0,]

datos$key_mod <- as.factor(paste0(datos$key," ",datos$tune.args))


#Create plots

#Crear una versin manual de viridis
vir_pal<- c("#fde725","#5ec962","#21918c","#3b528b","#440154")

#otra paleta blind friendly
#EVAL_palette <- c( '#4477AA', '#EE6677', '#228833', '#CCBB44', '#66CCEE', '#AA3377', '#BBBBBB')

#Edaphic variables

# AWCh
AWCh_plots<- 
  ggplot(filter(datos, var=="AWCh"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="AWCh")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,30)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

AWCh_plots

#CECSOL
CECSOL_plots<- 
  ggplot(filter(datos, var=="CECSOL"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="CECSOL")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,80)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

CECSOL_plots


#CLYPPT
CLYPPT_plots<- 
  ggplot(filter(datos, var=="CLYPPT"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="CLYPPT")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,75)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

CLYPPT_plots

#NITROGEN
NITROGEN_plots<- 
  ggplot(filter(datos, var=="NITROGEN"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="NITROGEN")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,17)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

NITROGEN_plots

#ORCDRC
ORCDRC_plots<- 
  ggplot(filter(datos, var=="ORCDRC"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="ORCDRC")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,300)+
    facet_wrap(~ species, scales="free", ncol=1, 
               strip.position="right")+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

ORCDRC_plots


#PHIHOX
PHIHOX_plots<- 
  ggplot(filter(datos, var=="PHIHOX"), aes(x=V1, y=p, color=top)) +
  geom_line(linewidth = 1)+
  labs(colour = "top", x="PHIHOX")+
  theme_classic()+ 
  scale_color_manual(values=vir_pal)+
  coord_cartesian(ylim=c(0,1))+
  scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
  xlim(40,90)+
  facet_wrap(~ species, scales="free", ncol=1, 
             strip.position="right")+
  theme(legend.position = "none",
        legend.title=element_blank(),
        legend.text = element_text(size=8),
        axis.text = element_text(size = 8),
        axis.title= element_text(size= 9),
        axis.title.y = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face="italic"),
        plot.margin = unit(c(0,0,0,0), "cm"),
        legend.box = "horizontal")

PHIHOX_plots


#Climatic variables

# Bio1
Bio1_plots<- 
  ggplot(filter(datos, var=="Bio1"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="Bio1")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,40)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

Bio1_plots

#Bio4
Bio4_plots<- 
  ggplot(filter(datos, var=="Bio4"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="Bio4")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,500)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

Bio4_plots


#Bio12
Bio12_plots<- 
  ggplot(filter(datos, var=="Bio12"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="Bio12")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,5000)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

Bio12_plots

#Bio14
Bio14_plots<- 
  ggplot(filter(datos, var=="Bio14"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="Bio14")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,175)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

Bio14_plots

#Bio15
Bio15_plots<- 
  ggplot(filter(datos, var=="Bio15"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="Bio15")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,150)+
    facet_wrap(~ species, scales="free", ncol=1, 
               strip.position="right")+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(face="italic"),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

Bio15_plots

#Extract common legend
library(rlang)

legend_summ <- get_legend(
  ORCDRC_plots + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.justification="center" ,
          legend.box.just = "bottom"))



while (!is.null(dev.list()))  dev.off()
graphics.off()

```


Create a single figure to summarize top5 model response curves and export it
```{r}

#Export new summary figure
summary_fig_soil_vars <- plot_grid(AWCh_plots,
                        CECSOL_plots,
                        CLYPPT_plots,
                        NITROGEN_plots,
                        ORCDRC_plots,
                        PHIHOX_plots,
                        legend_BSumm,
                        ncol = 6, nrow= 2, 
                        axis="l", rel_widths=1,
                        rel_heights=c(1,0.2), 
                        align="v", hjust=1, 
                        vjus=0.2)

summary_fig_bio_vars <- plot_grid(Bio1_plots,
                        Bio4_plots,
                        Bio12_plots,
                        Bio14_plots,
                        Bio15_plots,
                        legend_summ,
                        ncol = 5, nrow= 2, 
                        axis="l", rel_widths=1,
                        rel_heights=c(1,0.2), 
                        align="v", hjust=1, 
                        vjus=0.2)



path_save<-here("Modelos","TOP_modelos")

ggsave('summary_resp_top_new_soil_BS.pdf',
       plot= summary_fig_soil_vars, 
       width=9, height=5,
       dpi=600,
       units="in",
       path= path_BSave,
       device="pdf")

ggsave('summary_resp_top_new_bio_BS.pdf',
       plot= summary_fig_bio_vars, 
       width=7, height=5,
       dpi=600,
       units="in",
       path= path_save,
       device="pdf")




```


