---
title: "Response_curves_top5_edaphic-only data models"
author: "Laura J. Giraldo Kalil"
date: '2023-02-14'
output: html_document
---

This script summarizes the response curves for the "top 5" models
for each Damburneya species according to the environmental variables employed to build ecological niche models with MaxEnt.

It is based on the models generated in all other scripts
using edaphic data to model the niches of 
Damburneya species (D. ambigens, D. colorata, D. gentlei, D. salicifolia).

Those scripts are:
Combined climatic and edaphic data models:    "Model_Damb_bioclimsoil_02mar23.Rmd"
Climatic-only data models:                    "Model_Damb_bio_27feb23.Rmd"
Edaphic-only data models:                     "Model_Damb_soils_01mar23.Rmd"

It calls previously saved model files and the top 5 models previously chosen, based on delta AICc organized in decreasing order. It creates a summarized plot layout by species, and models type.

First, call the required libraries
```{r}

library(spocc)
library(spThin)
library(dismo)
library(rgeos)
library(ENMeval)
library(wallace)
library(here)
library(ggplot2)
library(gridExtra)
library(terra)
library(ade4)
library(dplyr)
library(gridtext)
library(cowplot)
library(ggpubr)
library(scales)
library(rcolorutils)
library(tidyverse)

```



Now, call the models for all the species. In this case, climatic-only models
```{r}
model_Da_soils <- readRDS(here("Modelos","soils_modelos","ambigens","model_Da_soils.rds"))

model_Dc_soils <- readRDS(here("Modelos","soils_modelos","colorata","model_Dc_new_soils.rds"))

model_Dg_soils <- readRDS(here("Modelos","soils_modelos","gentlei","model_Dg_soils.rds"))

model_Ds_soils <- readRDS(here("Modelos","soils_modelos","salicifolia","model_Ds_soils.rds"))


```



#D. ambigens


Generate response plots and data for the top models
MaxEnt response plots for D. ambigens are created for the chosen top 5 best models:
Da_top1   fc.LQHP_rm.2
Da_top2   fc.LQHP_rm.3
Da_top3   fc.LQHP_rm.2.5
Da_top4   fc.LQ_rm.1
Da_top5   fc.LQHP_rm.3.5


Da_top1   fc.LQHP_rm.2
```{r}
# Generate response plots for 1sth model for D. ambigens

pdf(here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top1.pdf"))
dismo::response(
  model_Da_soils@models$fc.LQ_rm.1,col="#CC3311",main="Da_S_top1_fc.LQ_rm.1", 
  expand=20,fun=function(x, y, ...) 
  predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Da_top1 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top1" , model="S", key="Da_S_top1")
CECSOL_resp_Da_top1 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top1" , model="S", key="Da_S_top1")
CLYPPT_resp_Da_top1 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top1" , model="S", key="Da_S_top1")
NITROGEN_resp_Da_top1 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top1" , model="S", key="Da_S_top1")
ORCDRC_resp_Da_top1 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top1" , model="S", key="Da_S_top1")
PHIHOX_resp_Da_top1 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top1" , model="S", key="Da_S_top1")


```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Da_S <-rbind(AWCh_resp_Da_top1, CECSOL_resp_Da_top1,
                        CLYPPT_resp_Da_top1, NITROGEN_resp_Da_top1, 
                        ORCDRC_resp_Da_top1, PHIHOX_resp_Da_top1) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top1_models_Da_S[soils_cols] <- lapply(top1_models_Da_S[soils_cols], factor)

#export response data
write.csv(top1_models_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top1.csv"))

#export model lambda

lambda_top1_Da_S <- as.data.frame(model_Da_soils@models$fc.LQ_rm.1@lambdas)
 
write.csv(lambda_top1_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","lambda_Da_S_top1.csv"))

```

Da_top2   fc.LQ_rm.1.5:

```{r}
# Generate response plots for 2nd model for D. ambigens

pdf(here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top2.pdf"))
dismo::response(
  model_Da_soils@models$fc.LQ_rm.1.5,col="#CC3311",main="Da_S_top2_fc.LQ_rm.1.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top2 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1.5,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top2" , model="S", key="Da_S_top2")
CECSOL_resp_Da_top2 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1.5,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...)))  %>% mutate(var="CECSOL", species="D. ambigens", top="top2" , model="S", key="Da_S_top2")
CLYPPT_resp_Da_top2 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1.5,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top2" , model="S", key="Da_S_top2")
NITROGEN_resp_Da_top2 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1.5,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top2" , model="S", key="Da_S_top2")
ORCDRC_resp_Da_top2 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1.5,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top2" , model="S", key="Da_S_top2")

PHIHOX_resp_Da_top2 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.1.5,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top2" , model="S", key="Da_S_top2")
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Da_S <-rbind(AWCh_resp_Da_top2, CECSOL_resp_Da_top2,
                        CLYPPT_resp_Da_top2, NITROGEN_resp_Da_top2, 
                        ORCDRC_resp_Da_top2, PHIHOX_resp_Da_top2) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top2_models_Da_S[soils_cols] <- lapply(top2_models_Da_S[soils_cols], factor)

#export response data
write.csv(top2_models_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top2.csv"))

#export model lambda

lambda_top2_Da_S <- as.data.frame(model_Da_soils@models$fc.LQ_rm.1.5@lambdas)
 
write.csv(lambda_top2_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","lambda_Da_S_top2.csv"))

```


Da_top3   fc.LQ_rm.2:

```{r}
# Generate response plots for 3rd model for D. ambigens

pdf(here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top3.pdf"))
dismo::response(
  model_Da_soils@models$fc.LQ_rm.2,col="#CC3311",main="Da_S_top3_fc.LQ_rm.2", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top3 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top3" , model="S", key="Da_S_top3")
CECSOL_resp_Da_top3 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top3" , model="S", key="Da_S_top3")
CLYPPT_resp_Da_top3 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top3" , model="S", key="Da_S_top3")
NITROGEN_resp_Da_top3 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top3" , model="S", key="Da_S_top3")
ORCDRC_resp_Da_top3 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top3" , model="S", key="Da_S_top3")

PHIHOX_resp_Da_top3 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top3" , model="S", key="Da_S_top3")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Da_S <-rbind(AWCh_resp_Da_top3, CECSOL_resp_Da_top3,
                        CLYPPT_resp_Da_top3, NITROGEN_resp_Da_top3, 
                        ORCDRC_resp_Da_top3, PHIHOX_resp_Da_top3) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top3_models_Da_S[soils_cols] <- lapply(top3_models_Da_S[soils_cols], factor)

#export response data
write.csv(top3_models_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top3.csv"))

#export model lambda

lambda_top3_Da_S <- as.data.frame(model_Da_soils@models$fc.LQ_rm.2@lambdas)
 
write.csv(lambda_top3_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","lambda_Da_S_top3.csv"))

```


Da_top4   fc.LQHP_rm.3.5

```{r}
# Generate response plots for 4th model for D. ambigens

pdf(here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top4.pdf"))
dismo::response(
  model_Da_soils@models$fc.LQHP_rm.3.5,col="#CC3311",main="Da_S_top4_fc.LQHP_rm.3.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top4 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQHP_rm.3.5,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top4" , model="S", key="Da_S_top4")
CECSOL_resp_Da_top4 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQHP_rm.3.5,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top4" , model="S", key="Da_S_top4")
CLYPPT_resp_Da_top4 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQHP_rm.3.5,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top4" , model="S", key="Da_S_top4")
NITROGEN_resp_Da_top4 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQHP_rm.3.5,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top4" , model="S", key="Da_S_top4")
ORCDRC_resp_Da_top4 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQHP_rm.3.5,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top4" , model="S", key="Da_S_top4")


PHIHOX_resp_Da_top4 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQHP_rm.3.5,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top4" , model="S", key="Da_S_top4")

```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Da_S <-rbind(AWCh_resp_Da_top4, CECSOL_resp_Da_top4,
                        CLYPPT_resp_Da_top4, NITROGEN_resp_Da_top4, 
                        ORCDRC_resp_Da_top4, PHIHOX_resp_Da_top4) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top4_models_Da_S[soils_cols] <- lapply(top4_models_Da_S[soils_cols], factor)

#export response data
write.csv(top4_models_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top4.csv"))

#export model lambda
lambda_top4_Da_S <- as.data.frame(model_Da_soils@models$fc.LQHP_rm.3.5@lambdas)
 
write.csv(lambda_top4_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","lambda_Da_S_top4.csv"))

```

Da_top5   fc.LQ_rm.2.5

```{r}
# Generate response plots for 5th model for D. ambigens

pdf(here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top5.pdf"))
dismo::response(
  model_Da_soils@models$fc.LQ_rm.2.5,col="#CC3311",main="Da_S_top5_fc.LQ_rm.2.5", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Da_top5 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2.5,var="AWCh",col="#CC3311",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. ambigens", top="top5" , model="S", key="Da_S_top5")
CECSOL_resp_Da_top5 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2.5,var="CECSOL",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. ambigens", top="top5" , model="S", key="Da_S_top5")
CLYPPT_resp_Da_top5 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2.5,var="CLYPPT",col="#CC3311",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. ambigens", top="top5" , model="S", key="Da_S_top5")
NITROGEN_resp_Da_top5 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2.5,var="NITROGEN",col="#CC3311",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. ambigens", top="top5" , model="S", key="Da_S_top5")
ORCDRC_resp_Da_top5 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2.5,var="ORCDRC",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. ambigens", top="top5" , model="S", key="Da_S_top5")

PHIHOX_resp_Da_top5 <- as.data.frame(dismo::response(
   model_Da_soils@models$fc.LQ_rm.2.5,var="PHIHOX",col="#CC3311",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. ambigens", top="top5" , model="S", key="Da_S_top5")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Da_S <-rbind(AWCh_resp_Da_top5, CECSOL_resp_Da_top5,
                        CLYPPT_resp_Da_top5, NITROGEN_resp_Da_top5, 
                        ORCDRC_resp_Da_top5, PHIHOX_resp_Da_top5) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top5_models_Da_S[soils_cols] <- lapply(top5_models_Da_S[soils_cols], factor)

#export response data
write.csv(top5_models_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","resp_Da_S_top5.csv"))

#export model lambda

lambda_top5_Da_S <- as.data.frame(model_Da_soils@models$fc.LQ_rm.2.5@lambdas)

write.csv(lambda_top5_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","lambda_Da_S_top5.csv"))

```



Create and export a single data frame with all response curves data of the top 5 models for D. ambigens
```{r}

top_models_Da_S <-rbind(top1_models_Da_S,top2_models_Da_S,
                        top3_models_Da_S,top4_models_Da_S,top5_models_Da_S)

write.csv(top_models_Da_S, here("Modelos","soils_modelos","ambigens","top_Da_S","top_models_Da_S.csv"))

```

#D. colorata

Generate response plots and data for the top models
MaxEnt response plots for D. colorata are created for the chosen top 5 best models:

Dc_top1		fc.LQHP_rm.2
Dc_top2		fc.LQP_rm.4
Dc_top3		fc.LQP_rm.3
Dc_top4		fc.LQHP_rm.4
Dc_top5		fc.L_rm.4


Dc_top1		fc.LQHP_rm.2
```{r}
# Generate response plots for 1sth model for D. colorata

pdf(here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top1.pdf"))
dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.2,col="#4477AA",main="Dc_S_top1_fc.LQHP_rm.2", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.2,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top1" , model="S", key="Dc_S_top1")

CECSOL_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.2,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top1" , model="S", key="Dc_S_top1")

CLYPPT_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.2,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top1" , model="S", key="Dc_S_top1")

NITROGEN_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.2,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top1" , model="S", key="Dc_S_top1")

ORCDRC_resp_Dc_top1 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.2,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top1" , model="S", key="Dc_S_top1")

PHIHOX_resp_Dc_top1 <- as.data.frame(dismo::response(
   model_Dc_soils@models$fc.LQHP_rm.2,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top1" , model="S", key="Dc_S_top1")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Dc_S <-rbind(AWCh_resp_Dc_top1, CECSOL_resp_Dc_top1,
                         CLYPPT_resp_Dc_top1, NITROGEN_resp_Dc_top1, 
                         ORCDRC_resp_Dc_top1, PHIHOX_resp_Dc_top1) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top1_models_Dc_S[soils_cols] <- lapply(top1_models_Dc_S[soils_cols], factor)

#export response data
write.csv(top1_models_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top1.csv"))

#export model lambda

lambDc_top1_Dc_S <- as.data.frame(model_Dc_soils@models$fc.LQHP_rm.2@lambdas)

write.csv(lambDc_top1_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","lambDc_Dc_new_S_top1.csv"))

```



Dc_top2		fc.LQP_rm.4
```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top2.pdf"))
dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,col="#4477AA",main="Dc_S_top2_fc.LQP_rm.4", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top2" , model="S", key="Dc_S_top2")
CECSOL_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top2" , model="S", key="Dc_S_top2")
CLYPPT_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top2" , model="S", key="Dc_S_top2")
NITROGEN_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top2" , model="S", key="Dc_S_top2")
ORCDRC_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top2" , model="S", key="Dc_S_top2")
PHIHOX_resp_Dc_top2 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.4,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top2" , model="S", key="Dc_S_top2")
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Dc_S <-rbind(AWCh_resp_Dc_top2, CECSOL_resp_Dc_top2,
                         CLYPPT_resp_Dc_top2, NITROGEN_resp_Dc_top2, 
                         ORCDRC_resp_Dc_top2, PHIHOX_resp_Dc_top2) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top2_models_Dc_S[soils_cols] <- lapply(top2_models_Dc_S[soils_cols], factor)

#export response data
write.csv(top2_models_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top2.csv"))

#export model lambda

lambDc_top2_Dc_S <- as.data.frame(model_Dc_soils@models$fc.LQP_rm.4@lambdas)

write.csv(lambDc_top2_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","lambDc_Dc_new_S_top2.csv"))

```


Dc_top3		fc.LQP_rm.3
```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top3.pdf"))
dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,col="#4477AA",main="Dc_S_top3_fc.LQP_rm.3", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top3" , model="S", key="Dc_S_top3")
CECSOL_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top3" , model="S", key="Dc_S_top3")
CLYPPT_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top3" , model="S", key="Dc_S_top3")
NITROGEN_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top3" , model="S", key="Dc_S_top3")
ORCDRC_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top3" , model="S", key="Dc_S_top3")
PHIHOX_resp_Dc_top3 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQP_rm.3,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top3" , model="S", key="Dc_S_top3")
```





Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Dc_S <-rbind(AWCh_resp_Dc_top3, CECSOL_resp_Dc_top3,
                         CLYPPT_resp_Dc_top3, NITROGEN_resp_Dc_top3, 
                         ORCDRC_resp_Dc_top3, PHIHOX_resp_Dc_top3) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top3_models_Dc_S[soils_cols] <- lapply(top3_models_Dc_S[soils_cols], factor)

#export response data
write.csv(top3_models_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top3.csv"))

#export model lambda

lambDc_top3_Dc_S <- as.data.frame(model_Dc_soils@models$fc.LQP_rm.3@lambdas)

write.csv(lambDc_top3_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","lambDc_Dc_new_S_top3.csv"))

```



Dc_top4		fc.LQHP_rm.4
```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top4.pdf"))
dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,col="#4477AA",main="Dc_S_top4_fc.LQHP_rm.4", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top4" , model="S", key="Dc_S_top4")
CECSOL_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top4" , model="S", key="Dc_S_top4")
CLYPPT_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top4" , model="S", key="Dc_S_top4")
NITROGEN_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top4" , model="S", key="Dc_S_top4")
ORCDRC_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top4" , model="S", key="Dc_S_top4")
PHIHOX_resp_Dc_top4 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.LQHP_rm.4,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top4" , model="S", key="Dc_S_top4")
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Dc_S <-rbind(AWCh_resp_Dc_top4, CECSOL_resp_Dc_top4,
                         CLYPPT_resp_Dc_top4, NITROGEN_resp_Dc_top4, 
                         ORCDRC_resp_Dc_top4, PHIHOX_resp_Dc_top4) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top4_models_Dc_S[soils_cols] <- lapply(top4_models_Dc_S[soils_cols], factor)

#export response data
write.csv(top4_models_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top4.csv"))

#export model lambda

lambDc_top4_Dc_S <- as.data.frame(model_Dc_soils@models$fc.LQHP_rm.4@lambdas)

write.csv(lambDc_top4_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","lambDc_Dc_new_S_top4.csv"))

```


Dc_top5		fc.L_rm.4

```{r}
# Generate response plots for 1sth model for D. colorata
pdf(here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top5.pdf"))
dismo::response(
  model_Dc_soils@models$fc.L_rm.4,col="#4477AA",main="Dc_S_top5_fc.L_rm.4", 
  expand=20,fun=function(x, y, ...) 
    predict(x,y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.L_rm.4,var="AWCh",col="#4477AA",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. colorata", top="top5" , model="S", key="Dc_S_top5")
CECSOL_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.L_rm.4,var="CECSOL",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. colorata", top="top5" , model="S", key="Dc_S_top5")
CLYPPT_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.L_rm.4,var="CLYPPT",col="#4477AA",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. colorata", top="top5" , model="S", key="Dc_S_top5")
NITROGEN_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.L_rm.4,var="NITROGEN",col="#4477AA",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. colorata", top="top5" , model="S", key="Dc_S_top5")
ORCDRC_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.L_rm.4,var="ORCDRC",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. colorata", top="top5" , model="S", key="Dc_S_top5")
PHIHOX_resp_Dc_top5 <- as.data.frame(dismo::response(
  model_Dc_soils@models$fc.L_rm.4,var="PHIHOX",col="#4477AA",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. colorata", top="top5" , model="S", key="Dc_S_top5")
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Dc_S <-rbind(AWCh_resp_Dc_top5, CECSOL_resp_Dc_top5,
                         CLYPPT_resp_Dc_top5, NITROGEN_resp_Dc_top5, 
                         ORCDRC_resp_Dc_top5, PHIHOX_resp_Dc_top5) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top5_models_Dc_S[soils_cols] <- lapply(top5_models_Dc_S[soils_cols], factor)

#export response data
write.csv(top5_models_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","resp_Dc_new_S_top5.csv"))

#export model lambda

lambDc_top5_Dc_S <- as.data.frame(model_Dc_soils@models$fc.L_rm.4@lambdas)

write.csv(lambDc_top5_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","lambDc_Dc_new_S_top5.csv"))

```




Create and export a single data frame with all response curves data of the top 5 models for D. colorata
```{r}

top_models_Dc_S <-rbind(top1_models_Dc_S,top2_models_Dc_S,
                        top3_models_Dc_S,top4_models_Dc_S,top5_models_Dc_S)

write.csv(top_models_Dc_S, here("Modelos","soils_modelos","colorata","top_Dc_S","top_models_Dc_new_S.csv"))

```


# D. gentlei
Generate response plots and data for the top models
MaxEnt response plots for D. gentlei are created for the chosen top 5 best models:
Dg_top1   fc.LQH_rm.1
Dg_top2   fc.LQHP_rm.2.5
Dg_top3   fc.LQHP_rm.3
Dg_top4   fc.LQHP_rm.3.5
Dg_top5   fc.LQHP_rm.1


Dg_top1   fc.LQH_rm.1
  
```{r}
# Generate response plots for 1sth model for D. gentlei

pdf(here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top1.pdf"))
dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,col="#DDAA33", main="Dg_S_top1_fc.LQH_rm.1",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top1" , model="S", key="Dg_S_top1")
CECSOL_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top1" , model="S", key="Dg_S_top1")
CLYPPT_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top1" , model="S", key="Dg_S_top1")
NITROGEN_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top1" , model="S", key="Dg_S_top1")
ORCDRC_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top1" , model="S", key="Dg_S_top1")
PHIHOX_resp_Dg_top1 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQH_rm.1,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top1" , model="S", key="Dg_S_top1")
  
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Dg_S <-rbind(AWCh_resp_Dg_top1, CECSOL_resp_Dg_top1,
                         CLYPPT_resp_Dg_top1, NITROGEN_resp_Dg_top1, 
                         ORCDRC_resp_Dg_top1, PHIHOX_resp_Dg_top1) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top1_models_Dg_S[soils_cols] <- lapply(top1_models_Dg_S[soils_cols], factor)

#export response data
write.csv(top1_models_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top1.csv"))

#export model lambda

lambda_top1_Dg_S <- as.data.frame(model_Dg_soils@models$fc.LQH_rm.1@lambdas)

write.csv(lambda_top1_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","lambda_Dg_S_top1.csv"))

```


Dg_top2   fc.LQHP_rm.2.5:
```{r}
# Generate response plots for 2nd model for D. gentlei

pdf(here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top2.pdf"))
dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,col="#DDAA33", main="Dg_S_top2_fc.LQHP_rm.2.5",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top2" , model="S", key="Dg_S_top2")
CECSOL_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top2" , model="S", key="Dg_S_top2")
CLYPPT_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top2" , model="S", key="Dg_S_top2")
NITROGEN_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top2" , model="S", key="Dg_S_top2")
ORCDRC_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top2" , model="S", key="Dg_S_top2")
PHIHOX_resp_Dg_top2 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.2.5,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top2" , model="S", key="Dg_S_top2")
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Dg_S <-rbind(AWCh_resp_Dg_top2, CECSOL_resp_Dg_top2,
                         CLYPPT_resp_Dg_top2, NITROGEN_resp_Dg_top2, 
                         ORCDRC_resp_Dg_top2, PHIHOX_resp_Dg_top2) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top2_models_Dg_S[soils_cols] <- lapply(top2_models_Dg_S[soils_cols], factor)

#export response data
write.csv(top2_models_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top2.csv"))

#export model lambda

lambda_top2_Dg_S <- as.data.frame(model_Dg_soils@models$fc.LQHP_rm.2.5@lambdas)

write.csv(lambda_top2_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","lambda_Dg_S_top2.csv"))

```



Dg_top3   fc.LQHP_rm.3:
```{r}
# Generate response plots for 3rd model for D. gentlei

pdf(here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top3.pdf"))
dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,col="#DDAA33", main="Dg_S_top3_fc.LQHP_rm.3",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()


AWCh_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top3" , model="S", key="Dg_S_top3")
CECSOL_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top3" , model="S", key="Dg_S_top3")
CLYPPT_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top3" , model="S", key="Dg_S_top3")
NITROGEN_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top3" , model="S", key="Dg_S_top3")
ORCDRC_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top3" , model="S", key="Dg_S_top3")
PHIHOX_resp_Dg_top3 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top3" , model="S", key="Dg_S_top3")
```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Dg_S <-rbind(AWCh_resp_Dg_top3, CECSOL_resp_Dg_top3,
                         CLYPPT_resp_Dg_top3, NITROGEN_resp_Dg_top3, 
                         ORCDRC_resp_Dg_top3, PHIHOX_resp_Dg_top3) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top3_models_Dg_S[soils_cols] <- lapply(top3_models_Dg_S[soils_cols], factor)

#export response data
write.csv(top3_models_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top3.csv"))

#export model lambda

lambda_top3_Dg_S <- as.data.frame(model_Dg_soils@models$fc.LQHP_rm.3@lambdas)

write.csv(lambda_top3_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","lambda_Dg_S_top3.csv"))

```


Dg_top4   fc.LQHP_rm.3.5:
```{r}
# Generate response plots for 4th model for D. gentlei

pdf(here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top4.pdf"))
dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,col="#DDAA33", main="Dg_S_top4_fc.LQHP_rm.3.5",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top4" , model="S", key="Dg_S_top4")
CECSOL_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top4" , model="S", key="Dg_S_top4")
CLYPPT_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top4" , model="S", key="Dg_S_top4")
NITROGEN_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top4" , model="S", key="Dg_S_top4")
ORCDRC_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top4" , model="S", key="Dg_S_top4")
PHIHOX_resp_Dg_top4 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.3.5,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top4" , model="S", key="Dg_S_top4")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Dg_S <-rbind(AWCh_resp_Dg_top4, CECSOL_resp_Dg_top4,
                         CLYPPT_resp_Dg_top4, NITROGEN_resp_Dg_top4, 
                         ORCDRC_resp_Dg_top4, PHIHOX_resp_Dg_top4) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top4_models_Dg_S[soils_cols] <- lapply(top4_models_Dg_S[soils_cols], factor)

#export response data
write.csv(top4_models_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top4.csv"))

#export model lambda

lambda_top4_Dg_S <- as.data.frame(model_Dg_soils@models$fc.LQHP_rm.3.5@lambdas)

write.csv(lambda_top4_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","lambda_Dg_S_top4.csv"))

```


Dg_top5   fc.LQHP_rm.1:
```{r}
# Generate response plots for 5th model for D. gentlei

pdf(here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top5.pdf"))
dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,col="#DDAA33", main="Dg_S_top5_fc.LQHP_rm.1",
  expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off ()


AWCh_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,var="AWCh",col="#DDAA33",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. gentlei", top="top5" , model="S", key="Dg_S_top5")
CECSOL_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,var="CECSOL",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. gentlei", top="top5" , model="S", key="Dg_S_top5")
CLYPPT_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,var="CLYPPT",col="#DDAA33",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. gentlei", top="top5" , model="S", key="Dg_S_top5")
NITROGEN_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,var="NITROGEN",col="#DDAA33",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. gentlei", top="top5" , model="S", key="Dg_S_top5")
ORCDRC_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,var="ORCDRC",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. gentlei", top="top5" , model="S", key="Dg_S_top5")
PHIHOX_resp_Dg_top5 <- as.data.frame(dismo::response(
  model_Dg_soils@models$fc.LQHP_rm.1,var="PHIHOX",col="#DDAA33",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. gentlei", top="top5" , model="S", key="Dg_S_top5")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Dg_S <-rbind(AWCh_resp_Dg_top5, CECSOL_resp_Dg_top5,
                         CLYPPT_resp_Dg_top5, NITROGEN_resp_Dg_top5, 
                         ORCDRC_resp_Dg_top5, PHIHOX_resp_Dg_top5) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top5_models_Dg_S[soils_cols] <- lapply(top5_models_Dg_S[soils_cols], factor)

#export response data
write.csv(top5_models_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","resp_Dg_S_top5.csv"))

#export model lambda

lambda_top5_Dg_S <- as.data.frame(model_Dg_soils@models$fc.LQHP_rm.1@lambdas)

write.csv(lambda_top5_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","lambda_Dg_S_top5.csv"))

```


Create and export a single data frame with all response curves data of the top 5 models for D. gentlei
```{r}

top_models_Dg_S <-rbind(top1_models_Dg_S,top2_models_Dg_S,
                        top3_models_Dg_S,top4_models_Dg_S,top5_models_Dg_S)

write.csv(top_models_Dg_S, here("Modelos","soils_modelos","gentlei","top_Dg_S","top_models_Dg_S.csv"))

```



#D. salicifolia
Generate response plots and data for the top models
MaxEnt response plots for D. salicifolia are created for the chosen top 5 best models:

Ds_top1   fc.LQHP_rm.1.5
Ds_top2   fc.LQHP_rm.1
Ds_top3   fc.LQH_rm.1.5
Ds_top4   fc.LQHP_rm.2
Ds_top5   fc.LQH_rm.2


Ds_top1   fc.LQHP_rm.1.5:
  
```{r}

pdf(here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top1.pdf"))
dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top1" , model="S", key="Ds_S_top1")
CECSOL_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top1" , model="S", key="Ds_S_top1")
CLYPPT_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top1" , model="S", key="Ds_S_top1")
NITROGEN_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top1" , model="S", key="Ds_S_top1")
ORCDRC_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top1" , model="S", key="Ds_S_top1")
PHIHOX_resp_Ds_top1 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1.5,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top1" , model="S", key="Ds_S_top1")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top1 model
top1_models_Ds_S <-rbind(AWCh_resp_Ds_top1, CECSOL_resp_Ds_top1,
                         CLYPPT_resp_Ds_top1, NITROGEN_resp_Ds_top1, 
                         ORCDRC_resp_Ds_top1, PHIHOX_resp_Ds_top1) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top1_models_Ds_S[soils_cols] <- lapply(top1_models_Ds_S[soils_cols], factor)

#export response data
write.csv(top1_models_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top1.csv"))

#export model lambda

lambda_top1_Ds_S <- as.data.frame(model_Ds_soils@models$fc.LQHP_rm.1.5@lambdas)

write.csv(lambda_top1_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","lambda_Ds_S_top1.csv"))

```


Ds_top2   fc.LQHP_rm.1:
  
```{r}
pdf(here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top2.pdf"))
dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top2" , model="S", key="Ds_S_top2")
CECSOL_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top2" , model="S", key="Ds_S_top2")
CLYPPT_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top2" , model="S", key="Ds_S_top2")
NITROGEN_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top2" , model="S", key="Ds_S_top2")
ORCDRC_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top2" , model="S", key="Ds_S_top2")
PHIHOX_resp_Ds_top2 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.1,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top2" , model="S", key="Ds_S_top2")
```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top2 model
top2_models_Ds_S <-rbind(AWCh_resp_Ds_top2, CECSOL_resp_Ds_top2,
                         CLYPPT_resp_Ds_top2, NITROGEN_resp_Ds_top2, 
                         ORCDRC_resp_Ds_top2, PHIHOX_resp_Ds_top2) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top2_models_Ds_S[soils_cols] <- lapply(top2_models_Ds_S[soils_cols], factor)

#export response data
write.csv(top2_models_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top2.csv"))

#export model lambda

lambda_top2_Ds_S <- as.data.frame(model_Ds_soils@models$fc.LQHP_rm.1@lambdas)

write.csv(lambda_top2_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","lambda_Ds_S_top2.csv"))

```


Ds_top3   fc.LQH_rm.1.5:
  
```{r}

pdf(here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top3.pdf"))
dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top3" , model="S", key="Ds_S_top3")
CECSOL_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top3" , model="S", key="Ds_S_top3")
CLYPPT_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top3" , model="S", key="Ds_S_top3")
NITROGEN_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top3" , model="S", key="Ds_S_top3")
ORCDRC_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top3" , model="S", key="Ds_S_top3")
PHIHOX_resp_Ds_top3 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.1.5,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top3" , model="S", key="Ds_S_top3")

```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top3 model
top3_models_Ds_S <-rbind(AWCh_resp_Ds_top3, CECSOL_resp_Ds_top3,
                         CLYPPT_resp_Ds_top3, NITROGEN_resp_Ds_top3, 
                         ORCDRC_resp_Ds_top3, PHIHOX_resp_Ds_top3) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top3_models_Ds_S[soils_cols] <- lapply(top3_models_Ds_S[soils_cols], factor)

#export response data
write.csv(top3_models_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top3.csv"))

#export model lambda

lambda_top3_Ds_S <- as.data.frame(model_Ds_soils@models$fc.LQH_rm.1.5@lambdas)

write.csv(lambda_top3_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","lambda_Ds_S_top3.csv"))

```



Ds_top4   fc.LQHP_rm.2:
  
```{r}
pdf(here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top4.pdf"))
dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top4" , model="S", key="Ds_S_top4")
CECSOL_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top4" , model="S", key="Ds_S_top4")
CLYPPT_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top4" , model="S", key="Ds_S_top4")
NITROGEN_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top4" , model="S", key="Ds_S_top4")
ORCDRC_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top4" , model="S", key="Ds_S_top4")
PHIHOX_resp_Ds_top4 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQHP_rm.2,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top4" , model="S", key="Ds_S_top4")

```

Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top4 model
top4_models_Ds_S <-rbind(AWCh_resp_Ds_top4, CECSOL_resp_Ds_top4,
                         CLYPPT_resp_Ds_top4, NITROGEN_resp_Ds_top4, 
                         ORCDRC_resp_Ds_top4, PHIHOX_resp_Ds_top4) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top4_models_Ds_S[soils_cols] <- lapply(top4_models_Ds_S[soils_cols], factor)

#export response data
write.csv(top4_models_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top4.csv"))

#export model lambda

lambda_top4_Ds_S <- as.data.frame(model_Ds_soils@models$fc.LQHP_rm.2@lambdas)

write.csv(lambda_top4_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","lambda_Ds_S_top4.csv"))

```



Ds_top5   fc.LQH_rm.2:
  
```{r}
pdf(here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top5.pdf"))
dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2
  ,col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))
dev.off()

AWCh_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2
  ,var="AWCh",col="#44AA99",expand=20,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="AWCh", species="D. salicifolia", top="top5" , model="S", key="Ds_S_top5")
CECSOL_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2
  ,var="CECSOL",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CECSOL", species="D. salicifolia", top="top5" , model="S", key="Ds_S_top5")
CLYPPT_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2
  ,var="CLYPPT",col="#44AA99",expand=1000,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="CLYPPT", species="D. salicifolia", top="top5" , model="S", key="Ds_S_top5")
NITROGEN_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2
  ,var="NITROGEN",col="#44AA99",fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="NITROGEN", species="D. salicifolia", top="top5" , model="S", key="Ds_S_top5")
ORCDRC_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2
  ,var="ORCDRC",col="#44AA99",expand=50,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="ORCDRC", species="D. salicifolia", top="top5" , model="S", key="Ds_S_top5")
PHIHOX_resp_Ds_top5 <- as.data.frame(dismo::response(
  model_Ds_soils@models$fc.LQH_rm.2,var="PHIHOX",col="#44AA99",expand=100,fun=function(x, y, ...) predict(x, y, args="doclamp=FALSE", ...))) %>% mutate(var="PHIHOX", species="D. salicifolia", top="top5" , model="S", key="Ds_S_top5")
```


Export useful information from the model: response data and lambda
```{r}

#join response data for variables of top5 model
top5_models_Ds_S <-rbind(AWCh_resp_Ds_top5, CECSOL_resp_Ds_top5,
                         CLYPPT_resp_Ds_top5, NITROGEN_resp_Ds_top5, 
                         ORCDRC_resp_Ds_top5, PHIHOX_resp_Ds_top5) 

#factorize categorical columns
soils_cols <- c("var","species","top","model","key")
top5_models_Ds_S[soils_cols] <- lapply(top5_models_Ds_S[soils_cols], factor)

#export response data
write.csv(top5_models_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","resp_Ds_S_top5.csv"))

#export model lambda

lambda_top5_Ds_S <- as.data.frame(model_Ds_soils@models$fc.LQH_rm.2@lambdas)

write.csv(lambda_top5_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","lambda_Ds_S_top5.csv"))

```



Create and export a single data frame with all response curves data of the top 5 models for D. salicifolia
```{r}

top_models_Ds_S <-rbind(top1_models_Ds_S,top2_models_Ds_S,
                        top3_models_Ds_S,top4_models_Ds_S,top5_models_Ds_S)

write.csv(top_models_Ds_S, here("Modelos","soils_modelos","salicifolia","top_Ds_S","top_models_Ds_S.csv"))

```



Create and export a single data frame with all response curves data of the top 5 models for all species
```{r}
#concatenate all models for all species in a single dataframe
top_models_all_S <-rbind(top_models_Da_S,
                         top_models_Dc_S,
                         top_models_Dg_S,
                         top_models_Ds_S)

write.csv(top_models_all_S,here("Modelos","soils_modelos",
                         "resp_top_models_all_new_S.csv"))

```

Edit data frame for plotting
```{r}

top_models_all_S <- 
  read.csv(here("Modelos","soils_modelos",
                         "resp_top_models_all_new_S.csv"))

#add the model name to the top 5 models based on a summary file
library(readxl)
tmp_summary_top <- read_xlsx(here("Modelos","TOP_modelos", "Resumen_top5_modelos.xlsx"))
colnames(tmp_summary_top)

cols_tmp <- c("ID","Model_data","model_key","Species","sp_key",
              "fc","rm","top","tune.args","key")
tmp_summary_top[cols_tmp] <- lapply(tmp_summary_top[cols_tmp], factor)


tmp_models <- subset(tmp_summary_top, Model_data %in% c("Edaphic-only"))
tmp_models <- tmp_models[,c("key","tune.args")]

#Call the top5 response dataframe and add columns with model name

top_models_all_S <- 
  left_join(top_models_all_S,tmp_models, by="key")

```


## Response plots edition
Response plot layout of the top 5 models by species and model, in ggplot



Create de plots for each variable with a plotting function


```{r}
#Reorder variables to avoid alphabetic order display

#top_models_all_S <- read.csv(here(
 # "Modelos","soils_modelos","resp_top_models_all_S.csv"))

neworder <- c("AWCh","CECSOL","CLYPPT","NITROGEN","ORCDRC","PHIHOX")

datos <- arrange(transform(top_models_all_S,
                           var=factor(var,levels=neworder)),var)



cols_tmp <- c("model","species","key",
             "top","tune.args")
datos[cols_tmp] <- lapply(datos[cols_tmp], factor)

# exclude data below or above the desired range in the layout
library(skimr)
skim(datos)

#exclude values lower than 0
datos <- datos[datos$V1 >= 0,]

datos$key_mod <- as.factor(paste0(datos$key," ",datos$tune.args))


#Create plots

#Crear una versin manual de viridis
vir_pal<- c("#fde725","#5ec962","#21918c","#3b528b","#440154")

#otra paleta blind friendly
EVAL_palette <- c( '#4477AA', '#EE6677', '#228833', '#CCBB44', '#66CCEE', '#AA3377', '#BBBBBB')


# AWCh
AWCh_plots<- 
  ggplot(filter(datos, var=="AWCh"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="AWCh")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,30)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

AWCh_plots

#CECSOL
CECSOL_plots<- 
  ggplot(filter(datos, var=="CECSOL"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="CECSOL")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,80)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

CECSOL_plots


#CLYPPT
CLYPPT_plots<- 
  ggplot(filter(datos, var=="CLYPPT"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="CLYPPT")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,75)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

CLYPPT_plots

#NITROGEN
NITROGEN_plots<- 
  ggplot(filter(datos, var=="NITROGEN"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="NITROGEN")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,17)+
    facet_wrap(~ species, scales="free", ncol=1)+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(face="italic", size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

NITROGEN_plots

#ORCDRC
ORCDRC_plots<- 
  ggplot(filter(datos, var=="ORCDRC"), aes(x=V1, y=p, color=top)) +
    geom_line(linewidth = 1)+
    labs(colour = "top", x="ORCDRC")+
    theme_classic()+ 
  scale_color_manual(values=vir_pal)+
    coord_cartesian(ylim=c(0,1))+
    scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
    xlim(0,300)+
    facet_wrap(~ species, scales="free", ncol=1, 
               strip.position="right")+
    theme(legend.position = "none",
          legend.title=element_blank(),
          legend.text = element_text(size=8),
          axis.text = element_text(size = 8),
          axis.title= element_text(size= 9),
          axis.title.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0,0,0,0), "cm"),
          legend.box = "horizontal")

ORCDRC_plots


#PHIHOX
PHIHOX_plots<- 
  ggplot(filter(datos, var=="PHIHOX"), aes(x=V1, y=p, color=top)) +
  geom_line(linewidth = 1)+
  labs(colour = "top", x="PHIHOX")+
  theme_classic()+ 
  scale_color_manual(values=vir_pal)+
  coord_cartesian(ylim=c(0,1))+
  scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1))+
  xlim(40,90)+
  facet_wrap(~ species, scales="free", ncol=1, 
             strip.position="right")+
  theme(legend.position = "none",
        legend.title=element_blank(),
        legend.text = element_text(size=8),
        axis.text = element_text(size = 8),
        axis.title= element_text(size= 9),
        axis.title.y = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face="italic"),
        plot.margin = unit(c(0,0,0,0), "cm"),
        legend.box = "horizontal")

PHIHOX_plots

#Extract common legend
library(rlang)

legend_summ <- get_legend(
  ORCDRC_plots + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.justification="center" ,
          legend.box.just = "bottom"))


while (!is.null(dev.list()))  dev.off()
graphics.off()

```
Create a single figure to summarize top5 model response curves and export it
```{r}

#Export new summary figure
summary_fig <- plot_grid(AWCh_plots,
                        CECSOL_plots,
                        CLYPPT_plots,
                        NITROGEN_plots,
                        ORCDRC_plots,
                        PHIHOX_plots,
                        legend_summ,
                        ncol = 6, nrow= 2, 
                        axis="l", rel_widths=1,
                        rel_heights=c(1,0.2), 
                        align="v", hjust=1, 
                        vjus=0.2)

path_save<-here("Modelos","TOP_modelos")

ggsave('summary_resp_top_new_S.pdf',
       plot= summary_fig, 
       width=9, height=5,
       dpi=600,
       units="in",
       path= path_save,
       device="pdf")

```


